Side-effects

### 2021-04-16 analysis/side-effects.Rmd

library(DT)
library(digest)
library(fs)
library(fst)
library(purrr)
library(tidyverse)
library(xtable)

@@

@@

```{r}
NE <- read_csv(
  PACKAGE_NORMALIZED_EXPRESSION_FILE,
  col_types = cols(
    minimized = col_character(),
    topcall = col_character(),
    is_model = col_double(),
    has_fundef = col_double(),
    has_calls = col_double(),
    has_assigns = col_double(),
    has_var = col_double(),
    has_bracket = col_double(),
    is_assign = col_double(),
    is_value = col_double(),
    is_ignore = col_double(),
    has_dollar = col_double(),
    has_user_call = col_double(),
    has_block = col_double(),
    has_meta_op = col_double(),
    normalized = col_character(),
    trimmed = col_character(),
    hash = col_character()
  )
) %>%
  select(
    minimized,
    topcall,
    normalized,
    expr_resolved_hash=hash
  )
```

>>>>

library(DT)
library(digest)
library(fs)
library(fst)
library(purrr)
library(tidyverse)
library(viridis)
library(xtable)

@@

## Types

```{r}
SEXP_TYPES <- tribble(
  ~type, ~type_name,
  0, "NILSXP",
  1, "SYMSXP",
  2, "LISTSXP",
  3, "CLOSXP",
  4, "ENVSXP",
  5, "PROMSXP",
  6, "LANGSXP",
  7, "SPECIALSXP",
  8, "BUILTINSXP",
  9, "CHARSXP",
  10, "LGLSXP",
  13, "INTSXP",
  14, "REALSXP",
  15, "CPLXSXP",
  16, "STRSXP",
  17, "DOTSXP",
  18, "ANYSXP",
  19, "VECSXP",
  20, "EXPRSXP",
  21, "BCODESXP",
  22, "EXTPTRSXP",
  23, "WEAKREFSXP",
  24, "RAWSXP",
  25, "S4SXP",
  30, "NEWSXP",
  31, "FREESXP",
  99, "FUNSXP"
) %>%
  mutate(
    type_name=str_replace(type_name, "SXP", "")
  )
```

```{r}
SE1 <- left_join(SE, SEXP_TYPES, by="type") %>%
  select(-type) %>%
  rename(type=type_name) %>%
  filter(event != "rvl") %>%
  mutate(
    stype=case_when(
      type == "CLO" ~ "Closure",
      type %in% c("STR","INT","LGL","RAW","REAL", "CPLX") ~ "Basic",
      type %in% c("ENV") ~ "Environment",
      type %in% c("VEC") ~ "List",
      type %in% c("SYM","LANG","EXPR") ~ "Expression",
      type %in% c("NIL") ~ "NULL",
      type %in% c("S4") ~ "S4",
      TRUE ~ "Other"
    )
  )

cs_count(SE1, stype)

class_type <- 
  SE1 %>%
  filter(event=="asn") %>%
  count(eval_call_srcref, stype, class, wt=N) %>% 
  count(class, stype)

cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

#class_type %>%
class_types_sites <-
  SE1 %>%
  filter(event=="asn") %>%
  cs_count(eval_call_srcref, class, stype, wt=N) %>% cs_count(class, stype)

class_types_sites %>%
  ggplot(aes(x=class, y=n, fill=stype)) + 
  geom_bar(stat="identity", position="fill", alpha=0.9) +
  scale_y_continuous(labels=scales::percent) +
#  scale_fill_viridis(discrete = TRUE, option="E") +
  scale_fill_manual(values = cbp1) +
  theme(text = element_text(size=19),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = .5),
        axis.title.y = element_blank(),
        aspect.ratio = 4/3,
        panel.grid.minor.x = element_blank(),
        legend.position="top") +
  labs(fill="")

ggsave(path(PLOT_DIR, "se-types.pdf"))
```

```{r}
types_sites <- 
  SE1 %>%
  filter(event=="asn") %>%
  cs_count(eval_call_srcref, class, stype, wt=N) %>% cs_count(stype)

closure_sites <- 
  SE1 %>%
  filter(event=="asn") %>%
  cs_count(eval_call_srcref, class, stype, wt=N) %>%
  filter(stype=="Closure") %>% 
  cs_count(class)

overview_table(
  r("Basic type ratio", percent(filter(types_sites, stype == "Basic")$p/100)),
  r("List type ratio", percent(filter(types_sites, stype == "List")$p/100)),
  r("Closure type ratio", percent(filter(types_sites, stype == "Closure")$p/100)),
  r("Closure type", filter(types_sites, stype == "Closure")$n),
  r("Closure type local", filter(closure_sites, class == "Local")$n)
)
```

@@

```{r eval=F}
NE <- read_csv(
  PACKAGE_NORMALIZED_EXPRESSION_FILE,
  col_types = cols(
    minimized = col_character(),
    topcall = col_character(),
    is_model = col_double(),
    has_fundef = col_double(),
    has_calls = col_double(),
    has_assigns = col_double(),
    has_var = col_double(),
    has_bracket = col_double(),
    is_assign = col_double(),
    is_value = col_double(),
    is_ignore = col_double(),
    has_dollar = col_double(),
    has_user_call = col_double(),
    has_block = col_double(),
    has_meta_op = col_double(),
    normalized = col_character(),
    trimmed = col_character(),
    hash = col_character()
  )
) %>%
  select(
    minimized,
    topcall,
    normalized,
    expr_resolved_hash=hash
  )
```
